Exercise 1: Software Architecture Description of the HS07 System

### 2008-02-04 SAiP/Module1/H1/doc/paper.tex
svn keyword testing
a bit of discussion stuff

\author{
  Anders H Poder, Jesper Dalberg, Lars Kringelbach\\\\
  Department of Computer Science, University of Aarhus\\
  Aabogade 34, 8200 {\AA}rhus N, Denmark\\\\
  \makeatletter
  \texttt{Group 11. Kilo}\\
  \texttt{19951439, 20074976, 20074842}\\
  \texttt{\{ahp, jdalberg, u074842\}@daimi.au.dk}
}

\date{$<<$Date: 2007/11/05 22:51:26 $>>$}

@@

The allocation viewpoint illustrates how components are deployed im actaual processes
within the HS07 system.

@@

@@

$<<$...$>>$

>>>>

\author{
  Anders H Poder, Jesper Dalberg, Lars Kringelbach\\\\
  Department of Computer Science, University of Aarhus\\
  Aabogade 34, 8200 {\AA}rhus N, Denmark\\\\
  \makeatletter
  \texttt{Group 11 - Kilo}\\
  \texttt{19951439, 20074976, 20074842}\\
  \texttt{\{ahp, jdalberg, u074842\}@daimi.au.dk}
}

\date{2008-02-04 13:32}

@@

The allocation viewpoint illustrates how components are deployed in actual processes
within the HS07 system.

@@

When performing reverse engineering to achieve an architectural description, the dangers
posed seem to be finding the correct balance in the choice of detail level. It
is easy to get to much information, cluttering the purpose of the 
AD, which in a basic sense is to clarify and present at wider understanding of
the system.

If you are a systems developer, a reverse engineered AD might help you understand 
the code better.

Experienced architects might recognize patterns emerging from the process, and 
immediately see possible design flaws in the implementation of these, thus
being able to help improve the next version of the system.

@@

$<<For the architectural description above, discuss what (if anything) should be changed or added for it to comply with the IEEE recommended practice for architectural description>>$

$<<Consider the definition of software architecture by [Perry and Wolf, 1992]. Discuss what the 'elements', 'form', and 'rationale' according to this definition would be for the HS07 system>>$

\cite{perrywolf1992} defines "elements" as three different classes, data elements, processing elements and connecting elements. In HS07 the data elements are temperatures, the processing element is the gateway and the connecting element is HTTP. The "form", as described by Perry and Wolf, is the choice of the observer pattern in HS07, and the "rationale" for doing so are defined by the Achitectural Requirements described elsewhere in this document.
